\huge Tor's Usability for Censorship Circumvention

### 2016-04-19 pets2017-paper/pets2017-paper.tex
Dashes.

\subsubsection{Rate of Success} 
5 more participants with the new interface were able to successfully circumvent censorship and connect to the Tor network. Due to the limited number of participants, this difference is not large enough to rule out the possibility of random chance being the cause for the difference. However, this does suggest that users are not less likely to succeed with the new interface based on the changes that were made. 
% impact of version on success: not significant (Mann-Whitney W = 5.5, p-value = 0.8248)
%impact of env on success: not significant (Kruskal-Wallis chi-squared = 4.7059, df = 2, p-value = 0.09509)

@@

\subsubsection{Time to Success} 
Although the median times to completion for participants of the new interface are less than those with the old interface (Table~\ref{table:participant-summary}), this difference is not statistically significant. The level of censorship had a significant impact on the time to success. The more difficult the censorship environment, the longer participants took to configure their connection (Kruskal-Wallis chi-squared = 80.926, df = 2, p-value < 2.2e-16). The distribution of participants' time to success can be seen in Figure~\ref{fig:time_to_success_clamped}.
%impact of version on time to success: not significant (W = 1569, p-value = 0.07796)
%impact of env on time to success : significant (Kruskal-Wallis chi-squared = 80.926, df = 2, p-value < 2.2e-16)

@@

The new interface results a statistically significant reduction in the overall active configuration time (Mann-Whitney Z = -3.055, p-value = 0.00225, effect size = 0.284), while maintaining the same probability for success for the user. We believe that getting rid of the technical bridge and proxy questions, instructing participants that they did not need a proxy, and simplifying the interface attributed to the reduction in time. 
%The impact of the environment on active time is significant (Kruskal-Wallis chi-squared = 51.978, df = 2, p-value = 5.166e-12)

>>>>

\subsubsection{Rate of Success} 
5 more participants with the new interface were able to successfully circumvent censorship and connect to the Tor network. Due to the limited number of participants, this difference is not large enough to rule out the possibility of random chance being the cause for the difference. However, this does suggest that users are not less likely to succeed with the new interface based on the changes that were made. 
% impact of version on success: not significant (Mann--Whitney W = 5.5, p-value = 0.8248)
%impact of env on success: not significant (Kruskal--Wallis chi-squared = 4.7059, df = 2, p-value = 0.09509)

@@

\subsubsection{Time to Success} 
Although the median times to completion for participants of the new interface are less than those with the old interface (Table~\ref{table:participant-summary}), this difference is not statistically significant. The level of censorship had a significant impact on the time to success. The more difficult the censorship environment, the longer participants took to configure their connection (Kruskal--Wallis chi-squared = 80.926, df = 2, p-value < 2.2e-16). The distribution of participants' time to success can be seen in Figure~\ref{fig:time_to_success_clamped}.
%impact of version on time to success: not significant (W = 1569, p-value = 0.07796)
%impact of env on time to success : significant (Kruskal--Wallis chi-squared = 80.926, df = 2, p-value < 2.2e-16)

@@

The new interface results a statistically significant reduction in the overall active configuration time (Mann--Whitney Z = -3.055, p-value = 0.00225, effect size = 0.284), while maintaining the same probability for success for the user. We believe that getting rid of the technical bridge and proxy questions, instructing participants that they did not need a proxy, and simplifying the interface attributed to the reduction in time. 
%The impact of the environment on active time is significant (Kruskal--Wallis chi-squared = 51.978, df = 2, p-value = 5.166e-12)
